\documentclass[12pt,a4paper,roman]{moderncv}   % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                        % style options are 'casual' (default) and 'classic' 
\moderncvcolor{blue}                          % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\rmdefault}    % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\usepackage{textcomp}

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
%\usepackage{CJKutf8}                         % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{3.000cm}           % if you want to change the width of the column with the dates

% personal data
\firstname{George}
\familyname{Shakhnazaryan}
\title{Software Engineer}               % optional, remove the line if not wanted
%\address{Lake Zurich, IL }{60047}    % optional, remove the line if not wanted
%\mobile{+1~(847)~555~5555}                     % optional, remove the line if not wanted
%\phone{+2~(345)~678~901}                      % optional, remove the line if not wanted
%\fax{+3~(456)~789~012}                        % optional, remove the line if not wanted
\email{gshakhn@gmail.com}                          % optional, remove the line if not wanted
\homepage{https://www.gshakhn.com}                    % optional, remove the line if not wanted
%\extrainfo{additional information}            % optional, remove the line if not wanted
%\photo[64pt][0.4pt]{picture}                  % '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{Objective: A technically challenging position in a team based environment.}                 % optional, remove the line if not wanted
	
\begin{document}
\maketitle

\section{Skills}
\cvitem{Core Languages}{Java, Scala}
\cvitem{Extra Languages}{JavaScript, Ruby, C\#}
\cvitem{Frameworks}{Stripes, Jersey, Scalatra, jQuery, Guice, \mbox{Hibernate}, Slick}
\cvitem{TDD Tools}{JUnit, ScalaTest, ScalaCheck, FitNesse, RSpec, Selenium WebDriver, \mbox{page-object}, Jasmine}
\cvitem{Quality Tools}{Sonar, Scalastyle, scct, Jenkins}
\cvitem{Databases}{Oracle 11g, HSQLDB 2.0, H2}
\cvitem{Source Control}{SVN, Git}
\cvitem{Other}{Dropwizard Metrics, Ant, Ivy, sbt, maven, Docker, Grafana, Splunk, \mbox{RabbitMQ}, Swagger}
%\cvitem{Operating Systems}{Linux, Windows, Mac OS X}
%\cvitem{Application Servers}{JBoss, Tomcat, IIS}
%\cvitem{IDEs}{IntelliJ, Visual Studio, Eclipse}
%\cvitem{Profilers}{YourKit, \mbox{EQATEC Profiler}}

\section{Experience}
\cventry{2010--Present}{Software Engineer}{Backstop Solutions Group}{Chicago, IL}{}{Software as a service platform for hedge funds and fund of funds.
\begin{itemize}
  \item Maintained and improved main Accounting/CRM Java web platform following Scrum and Kanban methodologies.
  \begin{itemize}
    \item Developed separate accounting service to make business logic more traceable. New service is an order of magnitude faster while using less resources.
    %\item Worked with product owners to write executable acceptance tests that caught numerous bugs during project development and subsequent maintenance.
    %\item Created scalable services to sync email from Exchange 2007/2010 and IMAP servers. The new services made syncing errors easier to diagnose.
    %\item Collaborated with product owners to figure out project priorities.
    \item Documented API endpoints for our clients to use via Swagger and Swagger UI.
    \item Trained new team members on platform and team processes.
    \item Coordinated biweekly Lunch and Learns for continuous education.
    \item Setup Vagrant recipe for development environment. This cut new developer setup time in half.
  \end{itemize}
  \item DevOps
  \begin{itemize}
    \item Deployed and monitored software in production.
    \item On call support for production servers.
    \item Integrated Dropwizard Metrics support to help monitor production. Trained others in how to add more metrics and view them in Grafana.
    %\item Puppet
  \end{itemize}
  \item Improved testing infrastructure to ease development.
  \begin{itemize}
    \item Integrated FitNesse with build process. Promoted writing integration tests and assisted team members in test writing.
    %\item Integrated Nailgun with integration test process. Sped up local integration test execution by an order of magnitude.
    \item Integrated js-test-driver with build process. This allowed us to test our JavaScript business logic separately from the web portion.
    \item Added new functionality and fixed bugs in page-object, a Ruby gem that provides a DSL for browser testing. page-object helped us write more readable tests.
    \item Wrote and helped others write RSpec tests using Selenium WebDriver and page-object.
    \item Modified RSpec Selenium WebDriver test runner to record videos of browser tests. This made diagnosing test failures easier.
  \end{itemize}
\end{itemize}
}

\cventry{2008-2010}{Software Developer}{AgileTek LLC}{Des Plaines, IL}{}{Custom software development firm specializing in high risk projects
\begin{itemize}
  \item Planned and estimated tasks, following an Agile methodology
  \item Created a .NET 3.5 WinForms application for an automated medical diagnostics device.
    \begin{itemize}
      \item Created a printing framework utilizing .NET printing to print reports. Designed and created reports using framework.
      \item Architected migration process of legacy data to new schema.
    \end{itemize}
  \item Created an online payment portal using ASP.NET Web Forms for auto \mbox{insurance} agencies, which thousands of customers use to pay for their auto insurance.
    \begin{itemize}
      \item Defined the client's objective and brainstormed ways of meeting the objective.
      \item Designed MS SQL Server database schema.
      \item Created FTP application to download payment records from a payment processor.
      \item Integrated multiple 3rd party software packages to ease client workflow.
      \item Setup SVN server and assisted team members in accessing source control.
    \end{itemize}
\end{itemize}}

\section{Education}
\cventry{2014}{Principles of Reactive Programming}{coursera.org}{}{}{}
\cventry{2012}{Functional Programming Principles in Scala}{coursera.org}{}{}{}
%\cventry{2012}{Artificial Intelligence for Robotics}{udacity.com}{}{}{An online course taught by Stanford professor Sebastian Thrun}
%\cventry{2011}{Introduction to Artificial Intelligence}{ai-class.com}{}{}{An online course taught by Stanford professors Peter Norvig and Sebastian Thrun}
\cventry{2006--2008}{Bachelor of Science}{University of Illinois at Chicago}{}{\textit{3.66/4.00}}{Major: Computer Science}

\section{Personal Projects}
\cventry{}{Lending Shak}{}{}{}{
  Android app that connects to a Prosper account to show balances and notes.
}
\cventry{}{checkin}{}{}{}{
  Meteor app that helps team members share status updates.
}
\cventry{}{private-wiki}{}{}{}{
  Scala.js app for taking notes. Currently in development.
}
\cventry{}{poke-analyzer}{}{}{}{
  Screenshot analyzer for Pokemon Go. Currently in development.
}


%\section{Languages}
%\cvitem{English}{Fluent}
%\cvitem{Russian}{Spoken}

\end{document}
